---
title: "Kaggle Airbnb Competition"
author: "Haoyu Wang"
date: "15/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set work dictionary
```{r}
getwd()
setwd('/Users/justin4love/Desktop/CU - Courses/5200 - Frameworks and Methods/Kaggle')
```
# Read data
```{r}
library(readr)
data = read_csv('analysisData.csv')
names(data)
```
# Removing price = 0
```{r}
data = data[!data$price==0,]
```
# Manually select useful columns by experience/ 32 zipcode, 48 weekly price, 49 monthly price,
```{r}
data_selected = data[, c(19,22,24:25,29,32,38:44,46:47,52:53,60:61,63:68,72,78,84,87,91)]
names(data_selected)
library(dplyr)
glimpse(data_selected)
```
# Study missing data for the data set
```{r}
library(visdat)
vis_miss(data_selected, warn_large_data = FALSE)
```
# Replace NA with median value in corresponding columns - first time cleaning
```{r}
data_selected = data_selected %>%
  mutate(host_total_listings_count = replace(host_total_listings_count, is.na(host_total_listings_count), 0)) %>%
  mutate(beds = replace(beds, is.na(beds), 0)) %>%
  mutate(reviews_per_month = replace(reviews_per_month, is.na(reviews_per_month),0)) %>%
  mutate(square_feet = replace(square_feet, is.na(square_feet),median(square_feet,na.rm = TRUE))) %>%
  mutate(zipcode = ifelse(nchar(zipcode)!=5,'Other',zipcode)) 
```

# Examine Missing value and Outlier
```{r}
library(skimr)
skim(data_selected)
library(summarytools)
print(dfSummary(data_selected,style='grid',graph.col = T),method = 'render')
```
# Replay the missing in corresponding columns - second time cleaning
```{r}
data_selected1 = data_selected %>%
  mutate(host_is_superhost = replace (host_is_superhost, is.na(host_is_superhost), TRUE)) %>%
  mutate(host_has_profile_pic = replace (host_has_profile_pic, is.na(host_has_profile_pic),
                                         TRUE)) %>%
  mutate(host_identity_verified = replace (host_identity_verified, is.na(host_identity_verified), TRUE)) %>%
  mutate(zipcode = replace (zipcode, is.na(zipcode), 'Other'))
```
# Check NA with all the columns selected for analysisdata
```{r}
sum(is.na(data_selected1))
```
# Isolate the numeric variable
```{r}
data_numeric = unlist(lapply(data_selected1, is.numeric))
data_numeric_dataframe = data_selected1[,data_numeric]
```

# Make a linear regression by only numeric variables
```{r}
model_numeric = lm(price~., data_numeric_dataframe)
```
# Multivariate Filter - all numeric variables seems GOOD now
```{r}
library(broom)
summary(model_numeric) %>%
  tidy()
```
# VIf check 
```{r}
library(car)
vif(model_numeric)
```
# Visualize VIF - availability_30/60/90 have seious multicollinearity
```{r}
data.frame(Predictor = names(vif(model_numeric)), VIF = vif(model_numeric)) %>%
  ggplot(aes(x=VIF, y = reorder(Predictor, VIF), fill=VIF))+
  geom_col()+
  geom_vline(xintercept=5, color = 'gray', size = 1.5)+
  geom_vline(xintercept = 10, color = 'red', size = 1.5)+
  scale_fill_gradient(low = '#fff7bc', high = '#d95f0e')+
  scale_y_discrete(name = "Predictor")+
  scale_x_continuous(breaks = seq(5,30,5))+
  theme_classic()
```
# Best Selection
```{r}
str(data_numeric_dataframe)
library(leaps)
subsets = regsubsets(price~.,data=data_numeric_dataframe, nvmax=23)
summary(subsets)
```
# names(summary(subsets)) - base on cp&bic&adjr2 21 variable should be used
# As the result we take of: availability_30
```{r}

subsets_measures = data.frame(model=1:length(summary(subsets)$cp),
                              cp=summary(subsets)$cp,
                              bic=summary(subsets)$bic, 
                              adjr2=summary(subsets)$adjr2)
subsets_measures
```
# Forward Selection
```{r}
start_mod = lm(price~1,data=data_numeric_dataframe)
empty_mod = lm(price~1,data=data_numeric_dataframe)
full_mod = lm(price~.,data=data_numeric_dataframe)
forwardStepwise = step(start_mod,
                       scope=list(upper=full_mod,lower=empty_mod),
                       direction='forward')
```
# Backward Selection
```{r}
start_mod = lm(price~.,data=data_numeric_dataframe)
empty_mod = lm(price~1,data=data_numeric_dataframe)
full_mod = lm(price~.,data=data_numeric_dataframe)
backwardStepwise = step(start_mod,
                        scope=list(upper=full_mod,lower=empty_mod),
                        direction='backward')
```
# Stepwise Variable Selection
```{r}
start_mod = lm(price~1,data=data_numeric_dataframe)
empty_mod = lm(price~1,data=data_numeric_dataframe)
full_mod = lm(price~.,data=data_numeric_dataframe)
hybridStepwise = step(start_mod,
                      scope=list(upper=full_mod,lower=empty_mod),
                      direction='both')
```
# New dataframe without availability_30 after Numeric Selection
```{r}
data_selected_FC = data_selected1[,-21]
```
# Use RandomForest method
```{r}
library(rpart); library(rpart.plot)
library(randomForest)
set.seed(617)
forest = randomForest(price~.,data=data_selected_FC,ntree = 1000)

```
# Read scoring data and apply model to generate predictions
```{r}
scoringData = read_csv('scoringData.csv')

str(scoringData$property_type)

scoringData <- scoringData %>%
  mutate(host_total_listings_count = replace(host_total_listings_count,
                                             is.na(host_total_listings_count),
                                             0))  %>%
  mutate(beds = replace(beds,
                        is.na(beds),
                        0))  %>%
  mutate(reviews_per_month = replace(reviews_per_month,
                                     is.na(reviews_per_month),
                                     0)) %>%
  mutate(square_feet = replace(square_feet, is.na(square_feet),median(square_feet,na.rm = TRUE)))%>%
  mutate(host_is_superhost = replace (host_is_superhost, is.na(host_is_superhost), TRUE)) %>%
  mutate(host_has_profile_pic = replace (host_has_profile_pic, is.na(host_has_profile_pic),
                                         TRUE)) %>%
  mutate(host_identity_verified = replace (host_identity_verified, is.na(host_identity_verified), TRUE)) %>%
  mutate(zipcode = parse_number(zipcode)) %>%
  mutate(zipcode = substring(zipcode,1,5)) %>%
  mutate(zipcode = ifelse(nchar(zipcode)!=5,'Other',zipcode)) %>%
  mutate(zipcode = replace (zipcode, is.na(zipcode), 'Other')) %>%         
  mutate(property_type= recode(property_type,
                                     Lighthouse = "Other",
                                     )) %>%
  mutate(property_type= recode(property_type,
                                     Timeshare = "Other",
                                     )) 
scoringData_1 = scoringData[,colnames(data_selected1[-15])]
scoringData_1 %>% 
  mutate(zipcode = ifelse(zipcode %in% unique(data_selected1$zipcode), zipcode, 'Other')) %>%
  mutate(property_type = ifelse(property_type %in% unique(data_selected1$property_type), 'Other'))
  
```
# Preparing matrix for Xgboost
```{r}
total = bind_rows(data_selected1, scoringData_1)

total$host_is_superhost = as.numeric(total$host_is_superhost)
total$host_has_profile_pic = as.numeric(total$host_has_profile_pic)
total$host_identity_verified = as.numeric(total$host_identity_verified)

region <- model.matrix(~neighbourhood_group_cleansed-1, total)
property <- model.matrix(~property_type-1, total)
room <- model.matrix(~room_type-1, total)
bed <- model.matrix(~bed_type-1, total)
cancellation <- model.matrix(~cancellation_policy-1, total)
zipcodes <- model.matrix(~zipcode-1, total)


total <- cbind(total, region, property, room, bed, cancellation, zipcodes)
total$neighbourhood_group_cleansed <- NULL; 
total$property_type <- NULL; 
total$room_type <- NULL
total$bed_type <- NULL
total$cancellation_policy <- NULL
total$zipcode <- NULL

```
# Make dataframe for AnalysisData and ScoringData after make them into matrix
```{r}
ds = total[!is.na(total$price),]
sd = total[is.na(total$price),]
```
# Take off price columns for both dataframes
```{r}
ds$price <- NULL
sd$price <- NULL
```
# Processing Xgboos method and test different nrounds
```{r}


data_selected1_ready <- data.matrix(ds)
library(xgboost)

params <- list(
  eta = 0.01,
  max_depth = 6,
  subsample = 0.8,
  min_child_weight = 7,
  colsample_bytree = 1
)
modelxgb <- xgboost(
  params = params,
  data = data_selected1_ready,
  label = data$price,
  nrounds = 4100,
  objective = "reg:linear"
)

pred = predict(modelxgb, as.matrix(sd))


submissionFile = data.frame(id = scoringData$id, price = pred)
write.csv(submissionFile, 'sample_submission_4100.csv',row.names = F)

```



